---
title: "MyShinyApp"
author: "Smoore"
date: "January 6, 2019"
output:  
  revealjs::revealjs_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

- The app developed for the first part of the assignment demo is avalilable at:  https://smoore.shinyapps.io/MyShinyAppandRepPitch/  

- Source code for ui.R and server.R files are available on the GitHub repo:  https://github.com/shawn0615/Shiny-Application-and-Reproducible-Pitch  

## Web Application functionality

- Enter trip distance and current price per gasoline to calculate total cost of gasoline used for each car.

- Enter budgeted cost for gasoline.

- Results displayed will show the car with Miles per Gallon(MPG) that are within your budget.

- Select desired car characteristic in term of : Cylinders and Transmission.

- Results displayed are selected cars that meet your criteria from main content with using the mtcars dataset from [R].

## Summary of mtcars datset

```{r mtcars, echo = TRUE}
summary(mtcars)
```

## Weight vs Mileage


```{r package, warning=FALSE, message=FALSE}
library("png")
library(plotly)
library(datasets)
# Get the input values.
input <- mtcars[,c('wt','mpg')]

# Plot the chart for cars with weight between 2.5 to 5 and mileage between 15 and 30.
plot_ly(x = input$wt,y = input$mpg,
   xlab = "Weight",
   ylab = "Milage",
   xlim = c(2.5,5),
   ylim = c(15,30),		 
   title = "Weight vs Mileage"
)


```




