---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Smoore"
date: "1/6/2019"
output: revealjs::revealjs_presentation
---

## Introduction

- This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

- The app developed for the first part of the assignment demo is avalilable at:

- Source code for ui.R and server.R files are available on the GitHub repo:

## Web Application functionality

- Enter trip distance and price per gasoline to calculate total cost of gasoline used for each car.

- Enter budgeted cost for gasoline.

- Results displayed will show the car with Miles per Gallon(MPG) that fit your budget.

- Select desired car characteristic in term of : Cylinders, Displacement, Horse Power and Transmission.

- Results displayed are selected cars that meet your criteria from main content with using the mtcars dataset from [R].

## Illiteracy Rates vs Income by State



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
```


```{r prerequisites}
rm(list=ls())
library(plotly)
```


```{r package, warning=FALSE, message=FALSE}

state_stats <- data.frame(State = state.abb, Income = as.vector(state.x77[,5]), Illiteracy= as.vector(state.x77[,3]), Pop=as.vector(state.x77[,1]), Grad=as.vector(state.x77[,6]), Region=state.name)

plot_ly(state_stats, x = ~ Income , y = ~ Illiteracy,  color=~Region, size=~Pop, type = "scatter")


```

